### 2025-07-05 Text/Thesis/Chapters/Chapter2.qmd
A detail in Chapter 2
thesis update

Statistical modeling plays a central role in the analysis of SAR imagery, where speckle is a fundamental characteristic. The main distributions considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which can describe varying levels of heterogeneity&nbsp;[@Frery1997].

@@

The $r$th order moments of the $\mathcal{G}_I^0$ model are
\begin{equation}
E\big(Z^r\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\frac{\Gamma(L+r)}{\Gamma(L)}, 
    \label{E:rmom}
\end{equation}
provided $\alpha <-r$, and infinite otherwise.
Therefore, assuming $\alpha<-1$, its expected value is
\begin{equation}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
    \label{E:mean1}
\end{equation}

Although the $\mathcal{G}_I^0$ distribution is defined by the parameters $\alpha$ and $\gamma$, in the SAR literature&nbsp;[@Nascimento2010] the texture $\alpha$ and the mean $\mu$ are usually used. Reparametrizing&nbsp;\eqref{E:gi01} with $\mu$, and denoting this model as $Z \sim \mathcal{G}_I^0(\alpha, \mu, L)$ we obtain:
\begin{equation}
    f_{\mathcal{G}^0_I}\bigl(z; \mu, \alpha, L \bigr) 
    = \frac{L^L\,\Gamma(L-\alpha)}
    {\bigl[-\mu(\alpha+1)\bigr]^{\alpha} \Gamma(-\alpha)\,\Gamma(L)}
    \frac{z^{L-1}}
    {\bigl[-\mu(\alpha+1)+Lz\bigr]^{L-\alpha}}
    \mathbbm 1_{\mathbbm R_+}(z), \label{E:gi02}
\end{equation}
The $\Gamma_{\mathrm{SAR}}$ model is a particular case of the $\mathcal{G}^0_I$ distribution, as demonstrated in&nbsp;[@Frery1997]. Specifically, for a given $\mu$ fixed,
$$
f_{\mathcal{G}^0_I}\big(z; \mu, \alpha, L\big)
\longrightarrow 
f_{\Gamma_{\text{SAR}}}(z;L, \mu) \quad \text{ when } \alpha\to-\infty.
$$

@@

In the context of SAR imaging, homogeneous areas produce fully developed speckle and are effectively modeled by the $Z \sim\Gamma_{\text{SAR}}(L, \mu)$ distribution. In contrast, textured or heterogeneous regions are better represented by the  $Z \sim\mathcal{G}^0_I(\mu, \alpha, L)$ model, where the roughness parameter $\alpha$ controls the degree of heterogeneity. Across this section, we show that all three entropy measures applied to $\mathcal{G}^0_I$ can be decomposed as:
\begin{equation}
\label{eq:decomp-intro}
\boxed{\;
\text{Entropy}\bigl(\mathcal{G}^{0}_{I}\bigr)
\;=\;
\text{Entropy}\bigl(\Gamma_{\mathrm{SAR}}\bigr)
\;+\;
\Delta_{\alpha}
\;}
\end{equation}

where  $\Delta_\alpha$ represents the \textit{excess entropy} induced by the roughness parameter $\alpha$. Notably, this excess vanishes in the homogeneous limit ($\alpha \to -\infty$), reducing \eqref{eq:decomp-intro} to the baseline case.

@@

### Rényi Entropy
For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
\begin{equation}
\label{E:entropy-R}
R_\lambda(Z)  = \frac{1}{1-\lambda }\ln \Bigl[ \mathbb{E}\Bigl( f^{\lambda - 1}(Z)\Bigr) \Bigr] =\frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
\end{equation}
As $\lambda \to 1$, $R_{\lambda}(Z)$ reduces to the Shannon entropy $H(Z)$.

@@

\textbf{Textured case.} Starting from the definition of Rényi entropy in  \eqref{E:entropy-R} and the pdf of  $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ given in \eqref{E:gi01}, we define:
$$
I
= \int_{0}^{\infty}\bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,dz
= C^{\lambda}
  \int_{0}^{\infty}
    \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,dz,
\qquad
C=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}.
$$
The parameterisation satisfies $\gamma=-\mu(\alpha+1)$, so the final result will be expressed in terms of $\mu$.

@@

        \bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,dz

@@

          \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,dz,

@@

With the change of variable $t=Lz/\gamma$ ($dz=\gamma\,dt/L$) we obtain:

@@

    \frac{t^{\lambda(L-1)}}{(1+t)^{\,\lambda(L-\alpha)}}\,dt.

@@

\int_{0}^{\infty}\frac{t^{a-1}}{(1+t)^{a+b}}\,dt

@@

For a continuous random variable $Z$ with pdf $f(z)$, the Tsallis entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
\begin{equation}
\label{eq:tsallis}
T_\lambda(Z) = \frac{1}{\lambda - 1} \mathbb{E} \Bigl[ 1 - (f(Z))^{\lambda - 1} \Bigr]
= \frac{1}{\lambda - 1} \Bigl[ 1 - \int_{-\infty}^{\infty} \bigl(f(z)\bigr)^{\lambda} dz \Bigr]. 
\end{equation}
In the limit $\lambda\to1$,
  $T_\lambda(Z)\to H(Z)$, making Tsallis a
  one-parameter generalisation of Shannon entropy.

@@

\textbf{Homogeneous case.} 
Let $Z\sim\Gamma_{\mathrm{SAR}}(L,\mu)$  with pdf given by \eqref{E:gamma1}. Define the integral:
\begin{equation*}
J
= \int_0^\infty \left[f_{\Gamma_{\text{SAR}}}(z;L,\mu)\right]^{\lambda} \, dz.
\end{equation*}
Substituting the density function and simplifying constants, we get
\begin{equation*}
J
= \left(\frac{L^L}{\Gamma(L)\,\mu^L}\right)^{\lambda}
  \int_0^\infty
     z^{\lambda(L-1)}
     \exp\left(-\frac{\lambda L}{\mu} z\right)\, dz.
\end{equation*}
Using the Gamma integral identity
\begin{align*}
\int_{0}^{\infty} x^{p-1}e^{-q x}\,\mathrm{d}x
&= \frac{\Gamma(p)}{q^{p}}, \quad p,q>0,
\end{align*}
with $p = \lambda(L-1) + 1$ and $q = \frac{\lambda L}{\mu}$. This leads to
\begin{equation*}
J
= \left(\frac{L^L}{\Gamma(L)\,\mu^L}\right)^{\lambda}
  \cdot
  \frac{\Gamma\big(\lambda(L-1)+1\big)}
       {\left(\frac{\lambda L}{\mu}\right)^{\lambda(L-1)+1}}.
\end{equation*}
After rearranging powers of $L$, $\mu$ and $\lambda$, we obtain
\begin{equation}
J
= \frac{L^{\lambda - 1}\,\mu^{1 - \lambda}\;
       \Gamma\big(\lambda(L - 1) + 1\big)}
      {\lambda^{\lambda(L - 1) + 1}\,
       \left[\Gamma(L)\right]^{\lambda}}.
\label{eq:Jgamma1}
\end{equation}
Substituting Equation \eqref{eq:Jgamma1} into the Tsallis entropy definition \eqref{eq:tsallis}, we have:
\begin{equation}
T_\lambda\big(\Gamma_{\text{SAR}}(L,\mu)\big)
= \frac{1}{\lambda - 1}
   \left[
     1 -
     \frac{L^{\lambda - 1}\,\mu^{1 - \lambda}\;
           \Gamma\big(\lambda(L - 1) + 1\big)}
          {\lambda^{\lambda(L - 1) + 1}\;
           \left[\Gamma(L)\right]^{\lambda}}
   \right].
\label{eq:TsallisGammaFinal1}
\end{equation}
This expression can also be written in an equivalent form:
<!-- \begin{equation*} -->
<!-- T_\lambda\big(\Gamma_{\text{SAR}}(L,\mu)\big) -->
<!-- = \frac{1}{\lambda - 1} \left[ -->
<!--    1 - -->
<!--    \mu^{1 - \lambda}\, -->
<!--    L^{\lambda - 1}\, -->
<!--    \lambda^{ - [\lambda(L - 1) + 1] }\, -->
<!--    \Gamma\big(\lambda(L - 1) + 1\big)\, -->
<!--    \Gamma(L)^{ - \lambda} -->
<!-- \right], -->
<!-- \end{equation*} -->
\begin{equation}
\label{eq:gammasar-Tsallis}
\boxed{%
\begin{aligned}
T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)=
\frac{1}{\lambda-1}\Bigl\{1-
\exp\Bigl[
(1-\lambda)\ln\mu
+(\lambda-1)\ln L
+\ln\Gamma\bigl(\lambda(L-1)+1\bigr) \\
-\lambda\ln\Gamma(L)
-(\lambda(L-1)+1)\ln\lambda
\Bigr]\Bigr\}.
\end{aligned}}
\end{equation}

\textbf{Textured case.} Starting from the Tsallis definition in \eqref{eq:tsallis} aand the pdf of $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ in \eqref{E:gi01}, define:

@@

J = \int_0^\infty \left[ f_{\mathcal{G}_I^0}(z) \right]^\lambda dz,

@@

J = \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
\int_0^\infty \frac{z^{\lambda(L-1)}}{(\gamma + Lz)^{\lambda(L - \alpha)}}  dz.

@@

Introducing the change of variables $t = \frac{Lz}{\gamma}$ (so that $z = \frac{\gamma t}{L}$ and $dz = \frac{\gamma}{L} dt$), we obtain

@@

J &= \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 

@@

{[\gamma(1 + t)]^{\lambda(L - \alpha)}}  dt\nonumber \\

@@

\int_0^\infty t^{\lambda(L-1)} (1 + t)^{-\lambda(L - \alpha)}  dt.

@@

\int_0^\infty \frac{t^{a-1}}{(1+t)^{a+b}} dt = B(a,b) = \frac{\Gamma(a)\Gamma(b)}{\Gamma(a+b)},

@@

J = \left[ \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right]^\lambda 

@@

J = [-\mu(\alpha + 1)]^{1-\lambda} L^{\lambda-1} 

@@

Figure&nbsp;\ref{fig:entropy-diagram} provides a conceptual overview of the decomposition structure of the differential entropy for the heterogeneous model $\mathcal{G}^0_I$. This entropy is expressed as the sum of a baseline term corresponding to the homogeneous $\Gamma_{\text{SAR}}$ distribution and an excess term $\Delta_\alpha$ that reflects the contribution of texture. The decomposition applies to the three entropy measures considered in this study: Shannon \eqref{eq:GIO-Sh1}, Rényi \eqref{eq-HGI0-R}, and Tsallis \eqref{eq:GI0-Tsallis}. In all cases, the excess term depends on the roughness parameter $\alpha$ and vanishes as $\alpha\to-\infty$, thus recovering the homogeneous case.
```{=latex}
\begin{figure}[H]
    \centering
    \begin{tikzpicture}[
    node distance=1.5cm,
    entropy/.style={rectangle, rounded corners, draw=blue!60, fill=blue!10, thick, minimum width=3cm, align=center, font=\sffamily},
    property/.style={rectangle, draw=orange!60, fill=orange!10, thick, minimum width=3cm, align=center, font=\sffamily},
    arrow/.style={-Stealth, thick}
    ]
    % Tu diagrama aquí...
    \node[entropy] (shannon) {Shannon \ $H(Z)$};
    \node[entropy, right=of shannon] (renyi) {Rényi \ $R_\lambda(Z)$};
    \node[entropy, right=of renyi] (tsallis) {Tsallis \ $T_\lambda(Z)$};

@@

Let $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ be an independent and identically distributed (i.i.d) random sample of size $n$ from drawn from a continuous distribution with cumulative distribution function (CDF) $F(z)$, let $Z_{(1)} \le Z_{(2)} \le \cdots \le Z_{(n)}$ denote the ordered sample, known as the order statistics.

@@

This result suggests that, under the true CDF, the transformed spacings are uniformly spread in expectation. Consequently, a simple density estimate around the point $Z_{(i)}$ can be motivated by the approximation:
$$
f(Z_{(i)}) \approx \frac{\text{mass}}{\text{length}} \approx \frac{1/(n+1)}{Z_{(i+1)} - Z_{(i)}},
$$
where $1/(n+1)$ serves as an estimate of the probability mass between $Z_{(i)}$ and $Z_{(i+1)}$.

@@

Let $F^{-1}(p)$ denote the quantile function (inverse CDF) of the distribution. We use $Q(p)$ as shorthand for $F^{-1}(p)$, so $Q:(0,1)\to \mathbb{R}$ satisfies $Q(p) = z$ if and only if $F(z) = p$.

Since $F(z)$ is monotonic, $Q(p)$ is differentiable wherever $f(z)$ is positive, with derivative $Q'(p) = \frac{d}{dp}F^{-1}(p)$. By the inverse function theorem, $Q'(p) = \frac{1}{f(Q(p))}$.

Starting from the definition of Shannon entropy in Equation \eqref{eq:entropy-sh}, a change of variables $p = F(z)$ can be applied. When $z = Q(p)$, it follows that $dz = Q'(p)\,dp$. Substituting into the integral:
\begin{align*}
  H(Z)
  &= -\int_{0}^{1} f(Q(p))\ln f(Q(p))\cdot Q'(p)\,dp \\
  &= -\int_{0}^{1} \ln f(Q(p))\,dp.
\end{align*}

Now using $f(Q(p)) = 1/Q'(p)$, we have $\ln f(Q(p)) = -\ln Q'(p)$. Thus:
\begin{equation}
  H(Z) = \int_{0}^{1} \ln Q'(p)\,dp = \int_{0}^{1} \ln \left(\frac{d}{dp}F^{-1}(p)\right) dp.
\end{equation}

@@

We consider the following entropy estimators variants, as discussed by Cassetti et al.&nbsp;[-@Cassetti2022].

@@

To facilitate nonparametric estimation, the expression in Equation \eqref{E:entropy-R} can be reformulated using the quantile function $Q(p) = F^{-1}(p)$, with $p \in (0,1)$. Applying the change of variable $z = Q(p)$ and noting that $f(Q(p)) = Q'(p)$ yields:
\begin{align*}
\int f^\lambda(z)\,dz
&= \int_0^1 [f(Q(p))]^\lambda \cdot Q'(p)\,dp \\
&= \int_0^1 [Q'(p)]^{1 - \lambda}\,dp.
\end{align*}
Substituting this into the original expression gives the quantile-based representation:
\begin{equation}
R_\lambda(Z) = \frac{1}{1 - \lambda} \ln \left( \int_0^1 [Q'(p)]^{1 - \lambda}\,dp \right).
\label{eq:renyi-quantile}
\end{equation}

@@

The definition of Tsallis entropy is given in Equation \eqref{eq:tsallis}, this expression can be reformulated using the quantile function $Q(p)=F^{-1}(p)$, defined for $p\in(0,1)$. Since $f(Q(p)) = 1/Q'(p)$, the expectation in \eqref{eq:tsallis} becomes
$$
  \mathbb{E}\bigl[f^{\lambda-1}(Z)\bigr] 
  = \int_{0}^{1} \bigl(Q'(p)\bigr)^{1-\lambda}\,dp,
$$
leading to the alternative representation:
\begin{equation}
  T_\lambda(Z)
  =\frac{1}{\lambda-1}
     \left\{
       1-\int_{0}^{1}\bigl(Q'(p)\bigr)^{1-\lambda}\,dp
     \right\}.
  \label{eq:Tsallis-quantile}
\end{equation}

>>>>

Statistical modeling plays a central role in the analysis of SAR imagery, where speckle is an inherent feature. For SAR intensity data, two main probability models are employed: the SAR-Gamma distribution ($\Gamma_{\text{SAR}}$), a reparameterization of the classical Gamma law suited to fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which can describe varying levels of heterogeneity&nbsp;[@Frery1997].

@@

The $r$th order moments of the $\mathcal{G}_I^0$ model are
\begin{equation}
E\big(Z^r\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\frac{\Gamma(L+r)}{\Gamma(L)}, 
    \label{E:rmom}
\end{equation}
provided that $\alpha <-r$, and infinite otherwise.
Therefore, assuming $\alpha<-1$, its expected value is
\begin{equation}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\frac{\Gamma(L+1)}{\Gamma(L)}=-\frac{\gamma}{\alpha+1}.
    \label{E:mean1}
\end{equation}

Although the $\mathcal{G}_I^0$ distribution is defined by the parameters $\alpha$ and $\gamma$, in the SAR literature&nbsp;[@Nascimento2010] the texture $\alpha$ and the mean $\mu$ are usually used. Reparameterizing&nbsp;\eqref{E:gi01} with $\mu$, and denoting this model as $Z \sim \mathcal{G}_I^0(\alpha, \mu, L)$ we obtain:
\begin{equation}
    f_{\mathcal{G}^0_I}\bigl(z; \mu, \alpha, L \bigr) 
    = \frac{L^L\,\Gamma(L-\alpha)}
    {\bigl[-\mu(\alpha+1)\bigr]^{\alpha} \Gamma(-\alpha)\,\Gamma(L)}
    \frac{z^{L-1}}
    {\bigl[-\mu(\alpha+1)+Lz\bigr]^{L-\alpha}}
    \mathbbm 1_{\mathbbm R_+}(z), \label{E:gi02}
\end{equation}
The $\Gamma_{\mathrm{SAR}}$ model is a particular case of the $\mathcal{G}^0_I$ distribution, as demonstrated in&nbsp;[@Frery1997]. Specifically, for a given $\mu$ fixed,
$$
f_{\mathcal{G}^0_I}\big(z; \mu, \alpha, L\big)
\longrightarrow 
f_{\Gamma_{\text{SAR}}}(z;L, \mu) \quad \text{ when } \alpha\to-\infty.
$$

@@

In the context of SAR imaging, homogeneous areas produce fully developed speckle and are effectively modeled by the $Z \sim\Gamma_{\text{SAR}}(L, \mu)$ distribution. In contrast, textured or heterogeneous regions are better represented by the  $Z \sim\mathcal{G}^0_I(\mu, \alpha, L)$ model, where the roughness parameter $\alpha$ controls the degree of heterogeneity. Across this section, we show that all three entropy measures applied to $\mathcal{G}^0_I$ can be decomposed as:
\begin{equation}
\label{eq:decomp-intro}
\boxed{\;
\text{Entropy}\bigl(\mathcal{G}^{0}_{I}\bigr)
\;=\;
\text{Entropy}\bigl(\Gamma_{\mathrm{SAR}}\bigr)
\;+\;
\Delta_{\alpha}
\;}
\end{equation}
where  $\Delta_\alpha$ represents the \textit{excess entropy} induced by the roughness parameter $\alpha$. Notably, this excess vanishes in the homogeneous limit ($\alpha \to -\infty$), reducing \eqref{eq:decomp-intro} to the baseline case.

@@

### Rényi Entropy
For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
\begin{equation}
\label{E:entropy-R}
R_\lambda(Z)  = \frac{1}{1-\lambda }\ln \Bigl[ \mathbb{E}\Bigl( f^{\lambda - 1}(Z)\Bigr) \Bigr] =\frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \,\mathrm{d}z.
\end{equation}
As $\lambda \to 1$, $R_{\lambda}(Z)$ reduces to the Shannon entropy $H(Z)$.

@@

\textbf{Textured case.} Starting from the definition of Rényi entropy in  \eqref{E:entropy-R} and the pdf of  $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ given in \eqref{E:gi01}, we define:
$$
I
= \int_{0}^{\infty}\bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,\mathrm{d}z
= C^{\lambda}
  \int_{0}^{\infty}
    \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,\mathrm{d}z,
\qquad
C=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}.
$$
The parameterisation satisfies $\gamma=-\mu(\alpha+1)$, so the final result will be expressed in terms of $\mu$.

@@

        \bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,\mathrm{d}z

@@

          \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,\mathrm{d}z,

@@

With the change of variable $t=Lz/\gamma$ ($\,\mathrm{d}z=\gamma\,\,\mathrm{d}t/L$) we obtain:

@@

    \frac{t^{\lambda(L-1)}}{(1+t)^{\,\lambda(L-\alpha)}}\,\mathrm{d}t.

@@

\int_{0}^{\infty}\frac{t^{a-1}}{(1+t)^{a+b}}\,\mathrm{d}t

@@

For a continuous random variable $Z$ with pdf $f(z)$, the Tsallis entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
\begin{equation}
\label{eq:tsallis}
T_\lambda(Z) = \frac{1}{\lambda - 1} \mathbb{E} \Bigl[ 1 - (f(Z))^{\lambda - 1} \Bigr]
= \frac{1}{\lambda - 1} \Bigl[ 1 - \int_{-\infty}^{\infty} \bigl(f(z)\bigr)^{\lambda} \,\mathrm{d}z \Bigr]. 
\end{equation}
In the limit $\lambda\to1$,
  $T_\lambda(Z)\to H(Z)$, making Tsallis a
  one-parameter generalization of Shannon entropy.

@@

\textbf{Homogeneous case.} 
Let $Z\sim\Gamma_{\mathrm{SAR}}(L,\mu)$  with pdf given by \eqref{E:gamma1}. Define the integral:
\begin{equation*}
I
= \int_0^\infty \left[f_{\Gamma_{\text{SAR}}}(z;L,\mu)\right]^{\lambda} \,\mathrm{d}z.
\end{equation*}
Substituting the density function and simplifying constants, we get
\begin{equation*}
I
= \left(\frac{L^L}{\Gamma(L)\,\mu^L}\right)^{\lambda}
  \int_0^\infty
     z^{\lambda(L-1)}
     \exp\left(-\frac{\lambda L}{\mu} z\right)\,\mathrm{d}z.
\end{equation*}
Using the Gamma integral identity
\begin{align*}
\int_{0}^{\infty} x^{p-1}e^{-q x}\,\mathrm{d}x
&= \frac{\Gamma(p)}{q^{p}}, \quad p,q>0,
\end{align*}
with $p = \lambda(L-1) + 1$ and $q = \frac{\lambda L}{\mu}$. This leads to
\begin{equation*}
I
= \left(\frac{L^L}{\Gamma(L)\,\mu^L}\right)^{\lambda}
  \cdot
  \frac{\Gamma\big(\lambda(L-1)+1\big)}
       {\left(\frac{\lambda L}{\mu}\right)^{\lambda(L-1)+1}}.
\end{equation*}
After rearranging powers of $L$, $\mu$ and $\lambda$, we obtain
\begin{equation}
I
= \frac{L^{\lambda - 1}\,\mu^{1 - \lambda}\;
       \Gamma\big(\lambda(L - 1) + 1\big)}
      {\lambda^{\lambda(L - 1) + 1}\,
       \left[\Gamma(L)\right]^{\lambda}}.
\label{eq:Jgamma1}
\end{equation}
Substituting Equation \eqref{eq:Jgamma1} into the Tsallis entropy definition \eqref{eq:tsallis}, we have:
\begin{equation}
T_\lambda\big(\Gamma_{\text{SAR}}(L,\mu)\big)
= \frac{1}{\lambda - 1}
   \left[
     1 -
     \frac{L^{\lambda - 1}\,\mu^{1 - \lambda}\;
           \Gamma\big(\lambda(L - 1) + 1\big)}
          {\lambda^{\lambda(L - 1) + 1}\;
           \left[\Gamma(L)\right]^{\lambda}}
   \right].
\label{eq:TsallisGammaFinal1}
\end{equation}
This expression can also be written in an equivalent form:
<!-- \begin{equation*} -->
<!-- T_\lambda\big(\Gamma_{\text{SAR}}(L,\mu)\big) -->
<!-- = \frac{1}{\lambda - 1} \left[ -->
<!--    1 - -->
<!--    \mu^{1 - \lambda}\, -->
<!--    L^{\lambda - 1}\, -->
<!--    \lambda^{ - [\lambda(L - 1) + 1] }\, -->
<!--    \Gamma\big(\lambda(L - 1) + 1\big)\, -->
<!--    \Gamma(L)^{ - \lambda} -->
<!-- \right], -->
<!-- \end{equation*} -->
\begin{equation}
\label{eq:gammasar-Tsallis}
\boxed{%
\begin{aligned}
T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)=
\frac{1}{\lambda-1}\Bigl\{1-
\exp\Bigl[
(1-\lambda)\ln\mu
+(\lambda-1)\ln L
+\ln\Gamma\bigl(\lambda(L-1)+1\bigr) \\
-\lambda\ln\Gamma(L)
-(\lambda(L-1)+1)\ln\lambda
\Bigr]\Bigr\}.
\end{aligned}}
\end{equation}

\textbf{Textured case.} Starting from the Tsallis definition in \eqref{eq:tsallis} and the pdf of $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ in \eqref{E:gi01}, define:

@@

I = \int_0^\infty \left[ f_{\mathcal{G}_I^0}(z) \right]^\lambda \,\mathrm{d}z,

@@

I = \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
\int_0^\infty \frac{z^{\lambda(L-1)}}{(\gamma + Lz)^{\lambda(L - \alpha)}}\,\mathrm{d}z.

@@

Introducing the change of variables $t = \frac{Lz}{\gamma}$ (so that $z = \frac{\gamma t}{L}$ and $\mathrm{d}z = \frac{\gamma}{L}\,\mathrm{d}t$), we obtain

@@

I &= \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 

@@

{[\gamma(1 + t)]^{\lambda(L - \alpha)}}\,\mathrm{d}t\nonumber \\

@@

\int_0^\infty t^{\lambda(L-1)} (1 + t)^{-\lambda(L - \alpha)}\,\mathrm{d}t.

@@

\int_0^\infty \frac{t^{a-1}}{(1+t)^{a+b}}\,\mathrm{d}z = B(a,b) = \frac{\Gamma(a)\Gamma(b)}{\Gamma(a+b)},

@@

I = \left[ \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right]^\lambda 

@@

I = [-\mu(\alpha + 1)]^{1-\lambda} L^{\lambda-1} 

@@

Figure&nbsp;\ref{fig:entropy-diagram} provides a conceptual overview of the decomposition structure of the differential entropy for the heterogeneous model $\mathcal{G}^0_I$. This entropy is expressed as the sum of a baseline term corresponding to the homogeneous $\Gamma_{\text{SAR}}$ distribution and an excess term $\Delta_\alpha$ that reflects the contribution of texture. The decomposition applies to the three entropy measures considered in this study: Shannon \eqref{eq:GIO-Sh1}, Rényi \eqref{eq-HGI0-R}, and Tsallis \eqref{eq:GI0-Tsallis}. In all cases, the excess term depends on the roughness parameter $\alpha$ and vanishes as $\alpha\to-\infty$, thus recovering the homogeneous case.
```{=latex}
\begin{figure}[H]
    \centering
    \begin{tikzpicture}[
    node distance=1.5cm,
    entropy/.style={rectangle, rounded corners, draw=blue!60, fill=blue!10, thick, minimum width=3cm, align=center, font=\sffamily},
    property/.style={rectangle, draw=orange!60, fill=orange!10, thick, minimum width=3cm, align=center, font=\sffamily},
    arrow/.style={-Stealth, thick}
    ]
    \node[entropy] (shannon) {Shannon \ $H(Z)$};
    \node[entropy, right=of shannon] (renyi) {Rényi \ $R_\lambda(Z)$};
    \node[entropy, right=of renyi] (tsallis) {Tsallis \ $T_\lambda(Z)$};

@@

Let $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ be an independent and identically distributed (i.i.d.) random sample of size $n$ from drawn from a continuous distribution with cumulative distribution function (cdf) $F(z)$, let $Z_{(1)} \le Z_{(2)} \le \cdots \le Z_{(n)}$ denote the ordered sample, known as the order statistics.

@@

This result suggests that, under the true cdf, the transformed spacings are uniformly spread in expectation. Consequently, a simple density estimate around the point $Z_{(i)}$ can be motivated by the approximation:
$$
f(Z_{(i)}) \approx \frac{\text{mass}}{\text{length}} \approx \frac{1/(n+1)}{Z_{(i+1)} - Z_{(i)}},
$$
where $1/(n+1)$ serves as an estimate of the probability mass between $Z_{(i)}$ and $Z_{(i+1)}$.

@@

Let $F^{-1}(p)$ denote the quantile function (inverse cdf) of the distribution. We use $Q(p)$ as shorthand for $F^{-1}(p)$, so $Q:(0,1)\to \mathbb{R}$ satisfies $Q(p) = z$ if and only if $F(z) = p$.

Since $F(z)$ is monotonic, $Q(p)$ is differentiable wherever $f(z)$ is positive, with derivative $Q'(p) = \frac{d}{\mathrm{d}p}F^{-1}(p)$. By the inverse function theorem, $Q'(p) = \frac{1}{f(Q(p))}$.

Starting from the definition of Shannon entropy in Equation \eqref{eq:entropy-sh}, a change of variables $p = F(z)$ can be applied. When $z = Q(p)$, it follows that $\mathrm{d}z = Q'(p)\,\mathrm{d}p$. Substituting into the integral:
\begin{align*}
  H(Z)
  &= -\int_{0}^{1} f(Q(p))\ln f(Q(p))\cdot Q'(p)\,\mathrm{d}p \\
  &= -\int_{0}^{1} \ln f(Q(p))\,\mathrm{d}p.
\end{align*}

Now using $f(Q(p)) = 1/Q'(p)$, we have $\ln f(Q(p)) = -\ln Q'(p)$. Thus:
\begin{equation}
  H(Z) = \int_{0}^{1} \ln Q'(p)\,\mathrm{d}p = \int_{0}^{1} \ln \left(\frac{d}{\mathrm{d}p}F^{-1}(p)\right)\,\mathrm{d}p.
\end{equation}

@@

We consider the following entropy estimators variants as discussed by Cassetti et al.&nbsp;[-@Cassetti2022].

@@

To facilitate nonparametric estimation, the expression in Equation \eqref{E:entropy-R} can be reformulated using the quantile function $Q(p) = F^{-1}(p)$, with $p \in (0,1)$. Applying the change of variable $z = Q(p)$ and noting that $f(Q(p)) = Q'(p)$ yields:
\begin{align*}
\int f^\lambda(z)\,\mathrm{d}z
&= \int_0^1 [f(Q(p))]^\lambda \cdot Q'(p)\,\mathrm{d}p \\
&= \int_0^1 [Q'(p)]^{1 - \lambda}\,\mathrm{d}p.
\end{align*}
Substituting this into the original expression gives the quantile-based representation:
\begin{equation}
R_\lambda(Z) = \frac{1}{1 - \lambda} \ln \left( \int_0^1 [Q'(p)]^{1 - \lambda}\,\mathrm{d}p \right).
\label{eq:renyi-quantile}
\end{equation}

@@

The definition of Tsallis entropy is given in Equation \eqref{eq:tsallis}, this expression can be reformulated using the quantile function $Q(p)=F^{-1}(p)$, defined for $p\in(0,1)$. Since $f(Q(p)) = 1/Q'(p)$, the expectation in \eqref{eq:tsallis} becomes
$$
  \mathbb{E}\bigl[f^{\lambda-1}(Z)\bigr] 
  = \int_{0}^{1} \bigl(Q'(p)\bigr)^{1-\lambda}\,\mathrm{d}p,
$$
leading to the alternative representation:
\begin{equation}
  T_\lambda(Z)
  =\frac{1}{\lambda-1}
     \left\{
       1-\int_{0}^{1}\bigl(Q'(p)\bigr)^{1-\lambda}\,\mathrm{d}p
     \right\}.
  \label{eq:Tsallis-quantile}
\end{equation}
